---
title: "data_cleanup_final_project"
author: "Carine Hajjar, Johannes Lang, Diego Arias"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(googlesheets4)
library(janitor)
library(stats)
library(fs)
library(readxl)
library(infer)
library(pracma)
```


```{r name cleaning}
dir_create("raw-data")

skirty <- read_excel("raw-data/data.xlsx")

skirty

# Here we cleaned the names and then gave them clearer names that work with r better:
y <- skirty%>%clean_names()%>%
  rename(gender_r = gender_2, 
         class_r = class_3, 
         extra_r = what_extracurriculars_are_you_most_involved_with_on_campus, 
         concentration_r = what_area_does_your_concentration_fall_into, 
         athlete_r = are_you_a_student_athlete, 
         international_r = are_you_an_international_student, 
         race_r = what_is_your_racial_ethnic_background, 
         urban_r = did_you_grow_up_in_a_rural_or_urban_area, 
         firstgen_r = do_you_identify_as_a_first_generation_student, 
         legacy_r = what_is_your_legacy_status, 
         religion_r = what_is_your_religious_background, 
         political_r = what_are_your_political_views, 
         
         gender_p1 = gender_14, 
         class_p1 = class_15, 
         extra_p1 = what_extracurriculars_are_they_most_involved_with_on_campus_16, 
         concentration_p1 = what_area_does_their_concentration_fall_into_17, 
         athlete_p1 = are_they_a_student_athlete_18, 
         international_p1 = are_they_an_international_student_19, 
         race_p1 = what_is_their_racial_ethnic_background_20, 
         urban_p1 = did_they_grow_up_in_a_rural_or_urban_area_21, 
         firstgen_p1 = do_they_identify_as_a_first_generation_student_22, 
         legacy_p1 = what_is_their_legacy_status_23, 
         religion_p1 = what_is_their_religious_background_24, 
         political_p1 = what_are_their_political_views_25, 
         
         gender_p2 = gender_26, 
         class_p2 = class_27, 
         extra_p2 = what_extracurriculars_are_they_most_involved_with_on_campus_28, 
         concentration_p2 = what_area_does_their_concentration_fall_into_29, 
         athlete_p2 = are_they_a_student_athlete_30, 
         international_p2 = are_they_an_international_student_31, 
         race_p2 = what_is_their_racial_ethnic_background_32, 
         urban_p2 = did_they_grow_up_in_a_rural_or_urban_area_33, 
         firstgen_p2 = do_they_identify_as_a_first_generation_student_34, 
         legacy_p2 = what_is_their_legacy_status_35, 
         religion_p2 = what_is_their_religious_background_36, 
         political_p2 = what_are_their_political_views_37, 
         
         
         gender_p3 = gender_38, 
         class_p3 = class_39, 
         extra_p3 = what_extracurriculars_are_they_most_involved_with_on_campus_40, 
         concentration_p3 = what_area_does_their_concentration_fall_into_41, 
         athlete_p3 = are_they_a_student_athlete_42, 
         international_p3 = are_they_an_international_student_43, 
         race_p3 = what_is_their_racial_ethnic_background_44, 
         urban_p3 = did_they_grow_up_in_a_rural_or_urban_area_45, 
         firstgen_p3 = do_they_identify_as_a_first_generation_student_46, 
         legacy_p3 = what_is_their_legacy_status_47, 
         religion_p3 = what_is_their_religious_background_48, 
         political_p3 = what_are_their_political_views_49, 
         
         gender_p4 = gender_50, 
         class_p4 = class_51, 
         extra_p4 = what_extracurriculars_are_they_most_involved_with_on_campus_52, 
         concentration_p4 = what_area_does_they_concentration_fall_into, 
         athlete_p4 = are_they_a_student_athlete_54, 
         international_p4 = are_they_an_international_student_55, 
         race_p4 = what_is_their_racial_ethnic_background_56, 
         urban_p4 = did_they_grow_up_in_a_rural_or_urban_area_57, 
         firstgen_p4 = do_they_identify_as_a_first_generation_student_58, 
         legacy_p4 = what_is_their_legacy_status_59, 
         religion_p4 = what_is_their_religious_background_60, 
         political_p4 = what_are_their_political_views_61)
```


```{r name same race column}
# We create a column to count the number of same race in a friend group and fill it with NAs:
m <- y%>%
  select(-s) %>%
  drop_na()%>%
  mutate(n_same_race= NA)

# Using a for loop, we go through the 67 friend groups and count the number of friends that have a race matching the respondent's race. Each time there's a match, a 1 is added to n_same_race which was created above. If no races match at all, the value in n_same_race will be 0:

for (i in 1:67) {

respondent_race<-m$race_r[i]

count=0

if(respondent_race==m$race_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_race==m$race_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_race==m$race_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_race==m$race_p4[i])
{count<-count+1}else{
count<-count}

m$n_same_race[i]<-count}
```


```{r same religion column}
# We create a column to count the number of same religions in a friend group and fill it with NAs:

m<-
  m%>%
  mutate(n_same_religion= NA)

# Using a for loop, we go through the 67 friend groups and count the number of friends that have a religion matching the respondent's religion. Each time there's a match, a 1 is added to n_same_religion which was created above. If no religions match at all, the value in n_same_religion will be 0: 

for (i in 1:67) {

respondent_religion<- m$religion_r[i]

count=0

if(respondent_religion==m$religion_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_religion==m$religion_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_religion==m$religion_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_religion==m$religion_p4[i])
{count<-count+1}else{
count<-count}

m$n_same_religion[i]<-count}

```

```{r same concentration}
# The process for race and religion above is repeated for concentrations: 

m<-
  m%>%
  mutate(n_same_concentration= NA)

for (i in 1:67) {

respondent_concentration<-m$concentration_r[i]

count=0

if(respondent_concentration==m$concentration_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_concentration==m$concentration_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_concentration==m$concentration_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_concentration==m$concentration_p4[i])
{count<-count+1}else{
count<-count}

m$n_same_concentration[i]<-count}
```



```{r athlete}
# the above process is repeated again as well. Here, however, I will walk you through the for loop a little more:
m<-
  m%>%
  mutate(n_same_athlete= NA)

# We are using the loop for each of the 68 rows-- 68 friend groups:

for (i in 1:67) {

respondent_athlete<-m$athlete_r[i]

count=0

# if the respondent answer matches the answer of p1, p2, p3, or p4, count +1 for each yes and +0 for each no:
if(respondent_athlete==m$athlete_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_athlete==m$athlete_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_athlete==m$athlete_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_athlete==m$athlete_p4[i])
{count<-count+1}else{
count<-count}

# we tally up the number of matches in the end:

m$n_same_athlete[i]<-count}
```

```{r international students}

# the same process above is repeated for international students:

m<-
  m%>%
  mutate(n_same_international= NA)

for (i in 1:67) {

respondent_international<-m$international_r[i]

count=0

if(respondent_international==m$international_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_international==m$international_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_international==m$international_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_international==m$international_p4[i])
{count<-count+1}else{
count<-count}

m$n_same_international[i]<-count}
```

```{r first gen}
# the process is done for first gen students:

m<-
  m%>%
  mutate(n_same_firstgen= NA)

for (i in 1:67) {

respondent_firstgen<-m$firstgen_r[i]

count=0

if(respondent_firstgen==m$firstgen_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_firstgen==m$firstgen_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_firstgen==m$firstgen_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_firstgen==m$firstgen_p4[i])
{count<-count+1}else{
count<-count}

m$n_same_firstgen[i]<-count}
```

```{r legacy}
# the process is done again to count up the number of first gen students in each friend group: 

m<-
  m%>%
  mutate(n_same_legacy= NA)

for (i in 1:67) {

respondent_legacy<-m$legacy_r[i]

count=0

if(respondent_legacy==m$legacy_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_legacy==m$legacy_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_legacy==m$legacy_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_legacy==m$legacy_p4[i])
{count<-count+1}else{
count<-count}

m$n_same_legacy[i]<-count}
```

```{r}
m <- m%>%
  mutate(urban_r=if_else(urban_r %in% c("Rural","rural"), "Rural","Urban"))%>%
  mutate(urban_p1=if_else(urban_p1 %in% c("Rural","rural"), "Rural","Urban"))%>%
  mutate(urban_p2=if_else(urban_p2 %in% c("Rural","rural"), "Rural","Urban"))%>%
  mutate(urban_p3=if_else(urban_p3 %in% c("Rural","rural"), "Rural","Urban"))%>%
  mutate(urban_p4=if_else(urban_p4 %in% c("Rural","rural"), "Rural","Urban"))

m<-
  m%>%
  mutate(n_same_urban= NA)

# Using a for loop, we go through the 67 friend groups and count the number of friends that have a urban matching the respondent's race. Each time there's a match, a 1 is added to n_same_race which was created above. If no races match at all, the value in n_same_race will be 0:

for (i in 1:67) {

respondent_urban<-m$urban_r[i]

count=0

if(respondent_urban==m$urban_p1[i])
{count<-count+1}else{
count<-count}

if(respondent_urban==m$urban_p2[i])
{count<-count+1}else{
count<-count}

if(respondent_urban==m$urban_p3[i])
{count<-count+1}else{
count<-count}

if(respondent_urban==m$urban_p4[i])
{count<-count+1}else{
count<-count}

m$n_same_urban[i]<-count}
```

```{r friend groups}
# we gather the data we refined and create a friend group data set. This counts the number of answers matching the respondent's in each friend group for each varible:
write.csv(m, 'm.csv')

friend_groups<-
  m%>%
  select(n_same_race, n_same_religion, n_same_concentration, n_same_athlete, n_same_international, n_same_firstgen, n_same_legacy)

```

```{r, some preliminary data visualization}

# this is a histogram for the observed number of white respondents and their number of white friends. We added the title, some color to the graph, adjusted binwidth, and captioned the graph. We do the same for the following races:

white_observed_histogram <- m%>%filter(race_r=="White")%>%
  ggplot(aes(x=n_same_race))+
  geom_histogram(binwidth=1, color = "darksalmon") + 
  geom_vline(xintercept = (.5127* 4), color = "red") +
  labs(title = "Observed Distribution of Same Race Friends for White Respondents", caption =  "the red line shows how our observed distribtuion compares to the expected \n mean when looking at the proportion of races in the total student body") +
  theme(plot.caption = element_text(hjust = 0, face = "italic"))



#write_rds(white_observed_histogram, "~/Desktop/GOV_1005/final_project_data_cleanup/rough-draft/o_white.rds")

# the same is done from above, but with Black or African American friends:
black_observed_histogram <- m%>%filter(race_r=="Black or African American")%>%
  ggplot(aes(x=n_same_race))+
  geom_histogram(binwidth=1, color = "darkblue") +
  geom_vline(xintercept = (.1117* 4), color = "red") +
  labs(title = "Observed Distribution of Same Race Friends for Black/African American Respondents", caption =  "the red line shows how our observed distribtuion compares to the expected \n mean when looking at the proportion of races in the total student body") +
  theme(plot.caption = element_text(hjust = 0, face = "italic"))


#write_rds(black_observed_histogram, "~/Desktop/GOV_1005/final_project_data_cleanup/rough-draft/o_black.rds")

# the same is done with Asian friends:
asian_observed_histogram <- m%>%filter(race_r=="Asian")%>%
  ggplot(aes(x=n_same_race))+
  geom_histogram(binwidth=1, color = "darkgreen") +
  geom_vline(xintercept = (.2283* 4), color = "red") +
  labs(title = "Observed Distribution of Same Race Friends for Asian Respondents", caption =  "the red line shows how our observed distribtuion compares to the expected \n mean when looking at the proportion of races in the total student body") +
  theme(plot.caption = element_text(hjust = 0, face = "italic"))

#write_rds(asian_observed_histogram, "~/Desktop/GOV_1005/final_project_data_cleanup/rough-draft/o_asian.rds")

# the same is done with Hispanic friends:
hispanic_observed_histogram <- m%>%filter(race_r=="Hispanic or Latino")%>%
  ggplot(aes(x=n_same_race))+
  geom_histogram(binwidth=1, color= "darkorange") + 
  geom_vline(xintercept = (.09933* 4), color = "red") +
  labs(title = "Observed Distribution of Same Race Friends for Hispanic/Latino Respondents", caption =  "the red line shows how our observed distribtuion compares to the expected \n mean when looking at the proportion of races in the total student body") +
  theme(plot.caption = element_text(hjust = 0, face = "italic"))

#write_rds(hispanic_observed_histogram, "~/Desktop/GOV_1005/final_project_data_cleanup/rough-draft/o_hispanic.rds")

# all of the histograms above will help us see the distribution of same race friends across different races and answer questions about if certain races self-segregate more than others. The violin plot below helps us do the same thing:

race_violin <- m %>%
  ggplot(aes(x=race_r, y = n_same_race, color =race_r)) +
  geom_violin() +
  stat_summary(fun.y = mean, geom = "point") +
  geom_jitter(shape = 16, color = "black", size = .5) + 
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Distribution of Same Race Friends per Respondent Race", y = "Number of Same Race Friends")

#write_rds(race_violin, "~/Desktop/GOV_1005/final_project_data_cleanup/rough-draft/race_violin.rds")

m %>%
  ggplot(aes(x=religion_r, y = n_same_religion, color =religion_r)) +
  geom_violin() +
  stat_summary(fun.y = mean, geom = "point") +
  geom_jitter(shape = 16, color = "black", size = .5)


```



rename(gender_r = gender_6, 
         class_r = class_7, 
         extra_r = what_extracurriculars_are_you_most_involved_with_on_campus, 
         concentration_r = what_area_does_your_concentration_fall_into, 
         athlete_r = are_you_a_student_athlete, 
         international_r = are_you_an_international_student, 
         race_r = what_is_your_racial_ethnic_background, 
         urban_r = did_you_grow_up_in_a_rural_or_urban_area, 
         firstgen_r = do_you_identify_as_a_first_generation_student, 
         legacy_r = what_is_your_legacy_status, 
         religion_r = what_is_your_religious_background, 
         political_r = what_are_your_political_views, 
         
         gender_p1 = gender_18, 
         class_p1 = class_19, 
         extra_p1 = what_extracurriculars_are_you_most_involved_with_on_campus_20, 
         concentration_p1 = what_area_does_your_concentration_fall_into_21, 
         athlete_p1 = are_you_a_student_athlete_22, 
         international_p1 = are_you_an_international_student_23, 
         race_p1 = what_is_your_racial_ethnic_background_24, 
         urban_p1 = did_you_grow_up_in_a_rural_or_urban_area_25, 
         firstgen_p1 = do_you_identify_as_a_first_generation_student_26, 
         legacy_p1 = what_is_your_legacy_status_27, 
         religion_p1 = what_is_your_religious_background_28, 
         political_p1 = what_are_your_political_views_29, 
         
         gender_p2 = gender_30, 
         class_p2 = class_31, 
         extra_p2 = what_extracurriculars_are_you_most_involved_with_on_campus_32, 
         concentration_p2 = what_area_does_your_concentration_fall_into_33, 
         athlete_p2 = are_you_a_student_athlete_34, 
         international_p2 = are_you_an_international_student_35, 
         race_p2 = what_is_your_racial_ethnic_background_36, 
         urban_p2 = did_you_grow_up_in_a_rural_or_urban_area_37, 
         firstgen_p2 = do_you_identify_as_a_first_generation_student_38, 
         legacy_p2 = what_is_your_legacy_status_39, 
         religion_p2 = what_is_your_religious_background_40, 
         political_p2 = what_are_your_political_views_41, 
         
         
         gender_p3 = gender_42, 
         class_p3 = class_43, 
         extra_p3 = what_extracurriculars_are_you_most_involved_with_on_campus_44, 
         concentration_p3 = what_area_does_your_concentration_fall_into_45, 
         athlete_p3 = are_you_a_student_athlete_46, 
         international_p3 = are_you_an_international_student_47, 
         race_p3 = what_is_your_racial_ethnic_background_48, 
         urban_p3 = did_you_grow_up_in_a_rural_or_urban_area_49, 
         firstgen_p3 = do_you_identify_as_a_first_generation_student_50, 
         legacy_p3 = what_is_your_legacy_status_51, 
         religion_p3 = what_is_your_religious_background_52, 
         political_p3 = what_are_your_political_views_53, 
         
         gender_p4 = gender_54, 
         class_p4 = class_55, 
         extra_p4 = what_extracurriculars_are_you_most_involved_with_on_campus_56, 
         concentration_p4 = what_area_does_your_concentration_fall_into_57, 
         athlete_p4 = are_you_a_student_athlete_58, 
         international_p4 = are_you_an_international_student_59, 
         race_p4 = what_is_your_racial_ethnic_background_60, 
         urban_p4 = did_you_grow_up_in_a_rural_or_urban_area_61, 
         firstgen_p4 = do_you_identify_as_a_first_generation_student_62, 
         legacy_p4 = what_is_your_legacy_status_63, 
         religion_p4 = what_is_your_religious_background_64, 
         political_p4 = what_are_your_political_views_65)

## preceptor
respondant George and four different rows for friends
the column for race 
then column for religion....

put race on same row

group by respondant 

block them in group of 5 