---
title: "data_cleanup_final_project"
author: "Carine Hajjar and Johannes Lang"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googlesheets4)
library(janitor)
library(stats)

```


```{r}
x%>%
  mutate("friend_group" = 1:68)%>%
  group_by(friend_group)
glimpse(x)

```



rename(gender_r = gender_6, 
         class_r = class_7, 
         extra_r = what_extracurriculars_are_you_most_involved_with_on_campus, 
         concentration_r = what_area_does_your_concentration_fall_into, 
         athlete_r = are_you_a_student_athlete, 
         international_r = are_you_an_international_student, 
         race_r = what_is_your_racial_ethnic_background, 
         urban_r = did_you_grow_up_in_a_rural_or_urban_area, 
         firstgen_r = do_you_identify_as_a_first_generation_student, 
         legacy_r = what_is_your_legacy_status, 
         religion_r = what_is_your_religious_background, 
         political_r = what_are_your_political_views, 
         
         gender_p1 = gender_18, 
         class_p1 = class_19, 
         extra_p1 = what_extracurriculars_are_you_most_involved_with_on_campus_20, 
         concentration_p1 = what_area_does_your_concentration_fall_into_21, 
         athlete_p1 = are_you_a_student_athlete_22, 
         international_p1 = are_you_an_international_student_23, 
         race_p1 = what_is_your_racial_ethnic_background_24, 
         urban_p1 = did_you_grow_up_in_a_rural_or_urban_area_25, 
         firstgen_p1 = do_you_identify_as_a_first_generation_student_26, 
         legacy_p1 = what_is_your_legacy_status_27, 
         religion_p1 = what_is_your_religious_background_28, 
         political_p1 = what_are_your_political_views_29, 
         
         gender_p2 = gender_30, 
         class_p2 = class_31, 
         extra_p2 = what_extracurriculars_are_you_most_involved_with_on_campus_32, 
         concentration_p2 = what_area_does_your_concentration_fall_into_33, 
         athlete_p2 = are_you_a_student_athlete_34, 
         international_p2 = are_you_an_international_student_35, 
         race_p2 = what_is_your_racial_ethnic_background_36, 
         urban_p2 = did_you_grow_up_in_a_rural_or_urban_area_37, 
         firstgen_p2 = do_you_identify_as_a_first_generation_student_38, 
         legacy_p2 = what_is_your_legacy_status_39, 
         religion_p2 = what_is_your_religious_background_40, 
         political_p2 = what_are_your_political_views_41, 
         
         
         gender_p3 = gender_42, 
         class_p3 = class_43, 
         extra_p3 = what_extracurriculars_are_you_most_involved_with_on_campus_44, 
         concentration_p3 = what_area_does_your_concentration_fall_into_45, 
         athlete_p3 = are_you_a_student_athlete_46, 
         international_p3 = are_you_an_international_student_47, 
         race_p3 = what_is_your_racial_ethnic_background_48, 
         urban_p3 = did_you_grow_up_in_a_rural_or_urban_area_49, 
         firstgen_p3 = do_you_identify_as_a_first_generation_student_50, 
         legacy_p3 = what_is_your_legacy_status_51, 
         religion_p3 = what_is_your_religious_background_52, 
         political_p3 = what_are_your_political_views_53, 
         
         gender_p4 = gender_54, 
         class_p4 = class_55, 
         extra_p4 = what_extracurriculars_are_you_most_involved_with_on_campus_56, 
         concentration_p4 = what_area_does_your_concentration_fall_into_57, 
         athlete_p4 = are_you_a_student_athlete_58, 
         international_p4 = are_you_an_international_student_59, 
         race_p4 = what_is_your_racial_ethnic_background_60, 
         urban_p4 = did_you_grow_up_in_a_rural_or_urban_area_61, 
         firstgen_p4 = do_you_identify_as_a_first_generation_student_62, 
         legacy_p4 = what_is_your_legacy_status_63, 
         religion_p4 = what_is_your_religious_background_64, 
         political_p4 = what_are_your_political_views_65)

## preceptor
respondant George and four different rows for friends
the column for race 
then column for religion....

put race on same row

group by respondant 

block them in group of 5 